Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies

### 2018-07-14 main.tex
removing old resolution study plot. new is complete
text updates (fixes) comment removal and updated plots

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe). This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds. Only 80\% of metals dominated by AGB enrichment are ejected through winds, even though 95\% of all metals leave the galaxy. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

@@

\section{Introduction}
% can I work "Currents of Space" into this paper somehow (Asimov)?
Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (review refs for obs and theory). One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x. stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas. (\textit{... more...})
% Discuss common modeling assumptions in CE models that
%    can be addressed here:
%        1) instantaneous recycling approximation
%        2) No metal mass loading of winds, or uniform 
%           loading across species
%        3) Uniform metal abundances across the ISM (one zone)
%
%  To some degree, cosmological simulations with comparably
%     low spatial resolution face the same problems, where
%     variations and spreads in abundances (esp. across 
%     species) can be smoothed over due to the low res. or
%     the particular details of the feedback methods and
%     yield injection methods.

One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references). While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (references), which plays an important role in determining the chemical properties of galaxies (references). % more on mixing
Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows. When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly. However, these processes are critical components in understanding galactic chemical evolution. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows. In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. (\textit{... more...}) That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

% Paragraphs
It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group. (APOGEE, GAIA, GALAH, RAVE? TGAS?). Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM. The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM. However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.

% Can shorten if this is actually going to be a letter
In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy. The simulation discussed here was first introduced in detail in Emerick et. al. 2018 (hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

@@

\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$. Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$. Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$). We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%. Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment. We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).

@@

\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}. We initialize a M$_{\rm gas} = 1.8 \times 10^{6} M_{\odot}$ disk with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$ using an exponential gas profile. The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc. Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium. The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy. Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero. Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.

\section{Results}
For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy. \textbf{UPDATE VALS:  In general, this galaxy has an average star formation rate of $4~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.  The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy. The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$. These winds eject 90\% of the metals produced in the galaxy, with 40\% of all metals leaving the virial radius by the end of the simulation time. }

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{SE_density.png}\\
\includegraphics[width=0.95\linewidth]{SE_z.png}
\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event. {\bf ignore SNIa line in plot -- need to remove}}
\label{fig:spatial distribution}
\end{figure}

@@

Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars. In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textbf{refs to canonical models}). Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances. In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models. However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies. To build towards this, we characterize the metal evolution and distributions in our galaxy below.

@@

We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF. We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element. This PDF is given as
\begin{align*}
  p(Z) = 
  \begin{cases}
    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right], 
    & Z < Z_{\rm{trans}} \\
    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
    N p_o Z^{-\alpha},
    & Z > Z_{\rm{trans}}
\end{cases}
\end{align*}
where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm trans}$ is the metal fraction at the transition between the log-normal and power-law components. When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm trans}$ as free parameters. These conditions set $N$ and $p_o$ to 
\begin{equation}
N = 
\end{equation}
and
\begin{equation}
p_o = \frac{1}{\sigma Z_{\rm trans} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm trans}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm trans}) \right]
\end{equation}.

We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex. We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{Scipy} \cite{Scipy}, stepping through possible values for $Z_{\rm trans}$, set to the centers of each of these bins. The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted. The log-normal + power-law PDF produces the best fit in nearly all cases.

We show in \ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases. These PDFs have been computed at an arbitrary single point in time, at 380 Myr. For clarity, we only show a subset of the 15 elements we follow. As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase. However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions. We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases. In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well. However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior. This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction. In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.

We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models. The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM. In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions. Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$. As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models. 
%Developing a complete physical model for what drives the formation and properties of $p(Z)$ is beyond the scope of this paper, but these prospects are discussed in Section~\ref{sec:discussion}.

%The log-normal distribution is a two parameter model defined by the log mean $M$ and the log standard deviation $S$. These values are related to the linear mean, $\mu$, and standard deviation, $\sigma$, as $\mu = e^{M+S^2/2}$ and $\sigma = e^{S^2 + 2M}(e^{S^2}-1)$. We define the log-normal distribution of metals in the ISM as a function of either the total metallicity $Z$ or the mass fraction of an individual metal species, $Z_i$, where $i$ denotes an individual element. For clarity in this section, we refer most often to total metallicity as the variable of interest. However, we note that any statement that applies to metallicity also applies to the mass fraction an individual metal species ($Z_i$). With these definitions, the log-normal metallicity PDF is given as
%\begin{equation}
%f(Z_i, M_i, S_i) = \frac{1}{\sqrt{2 \pi} S_i} \rm{exp}\left(\frac{-(ln(Z_i) - M_i)^2}{2S_i^2}\right).
%\end{equation}
%We can also specify the CDF of this distribution as 
%\begin{equation}
%F(Z_i, M_i, S_i) = \frac{1}{2} \left[1 + \rm{erf} \left(\frac{ln(Z_i) - M_i}{S_i \sqrt{2}} \right). \right].
%\end{equation}
%Thus, $F(Z_i, M_i, S_i)$ gives the fraction of mass in the ISM with metallicity $Z < Z_i$. For each of the 15 metal species in our simulations, and for each phase of the ISM, we compute the mass-weighted metal fraction PDFs and fit $f(Z_i,M_i,S_i)$ to each. In fitting, we find the parameters $M_i$ and $S_i$ for each distribution that minimizes the distance between the CDF from the simulations and the CDF from the log-normal fit, or $D_{\rm CDF}$. For consistency, we use equally spaced bins in log of 0.05 dex in every case.

%
% OLD TEXT - pre powerlaw
% We give the results of this fit in Figure~\ref{fig:log-normal} for the metal fraction PDFs of each element in the ISM as a whole. The PDFs computed directly from the simulation are shown in the top pane. Their log-normal best fits, and corresponding $D_{\rm CDF}$, are shown in the bottom panel. For clarity, we normalize each distribution by the peak (mode). In all cases, the metal mass fraction PDFs can be described with a log-normal distribution. This is a remarkable result. That the complex interplay between the dominant physical processes in the ISM, namely stellar feedback, turbulence, self-gravity, heating/cooling, and chemistry, produces metal distributions that are analytically tractable is surprising. Linking these instantaneous PDFs to a time evolution of the distributions parameters, $M_i$ and $S_i$, in a general way would create a powerful tool for modelling galactic chemical enrichment in semi-analytic models. This is beyond the scope of this work, but we discuss this further in Section~\ref{sec:discussion}.

% OLD TEXT ---- PRE powerlaw
%Upon closer inspection, we note that there are distinct differences with each metal and some noticeable deviations from true log-normality. Most elements have higher positive skew, tails towards higher metal fractions, than can be reasonable captured by a log-normal fit. Two elements in particular show quite broad distributions, N and Ba, which are less well fit by a log-normal as the other elements. As discussed earlier, these two elements have a distinct nucleosynthetic source, AGB winds, than the rest of the elements. Lower energy AGB winds generate broader enrichment distributions that are less well mixed than metals from core collapse and Type Ia supernovae. If this behavior is similar in star forming gas, we would expect elements from AGB winds to exhibit larger scatter in observed abundances. However, we note again that this figure represents all gas in the ISM. These deviations from log-normality and the high metallicity tails could be driven simply by grouping together qualitatively distinct phases of gas in the ISM, each with their own enrichment history. We investigate the metal fraction PDFs of individual gas phases below.

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}. For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.}
\label{fig:log-normal}
\end{figure*}

%\begin{figure*}
%\centering
%\includegraphics[width=0.95\linewidth]{lognorm_elements.png}
%\caption{The metal mass fraction PDF's binned directly from the simulation (top) for all 15 elements tracked in the simulation and the associated log-normal fits (bottom) along with the minimized CDF distance for each. Given the wide range in mass fractions among species, we normalize the PDFs by their peak for clarity. These PDFs are shown at 350~Myr into the 500~Myr simulation; the choice of time was arbitrary.}
%\label{fig:log-normal}
%\end{figure*}

% NOTES:
%    Discuss how generally good of fits these are but how some are less good. Mention how N and Ba are less well mixed (reference above) and how this should really be examined in sub-groups of the ISM, motivating the next section. Next section will plot mean and std of fits and distributions as function of time for each phase, along with chi-squared good-ness of fits values. Need to find a way to estimate / compute the uncertainty for this!! Poisson in each bin? shift bins a little and estimate variance this way?

%   Give the distributions of metals at ONE point in time in each phase for two elements, O and Ba. Show the log fit and the histogram on each (maybe use orange and blue?). Discuss how the distributions are well fit by lognormals and the evolution of each, giving values for the fits and using dashed lines showing mean/std of full distribution when not well fit by a lognormal.

@@

%\subsubsection{Log-normality in each Phase of the ISM}
%\label{sec:phase-pdfs}
The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude. The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary. Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM. In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time. We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.

>>>>

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe). This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds to the ISM. Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

@@

\section{Introduction}
% can I work "Currents of Space" into this paper somehow (Asimov)?
Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}). One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x. stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas. (\textit{... more...})
% Discuss common modeling assumptions in CE models that
%    can be addressed here:
%        1) instantaneous recycling approximation
%        2) No metal mass loading of winds, or uniform 
%           loading across species
%        3) Uniform metal abundances across the ISM (one zone)
%
%  To some degree, cosmological simulations with comparably
%     low spatial resolution face the same problems, where
%     variations and spreads in abundances (esp. across 
%     species) can be smoothed over due to the low res. or
%     the particular details of the feedback methods and
%     yield injection methods.

One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references). While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}). % more on mixing
Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows. When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly. However, these processes are critical components in understanding galactic chemical evolution. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillota2018}. In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group. (\textit{ references to APOGEE, GAIA, GALAH, RAVE, TGAS}). Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM. The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM. However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.

In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy. The simulation discussed here was first introduced in detail in Emerick et. al. 2018 (hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

@@

\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$. Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$. Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$). We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%. Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment. We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).

@@

\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}. We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$. The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc. Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium. The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy. Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero. Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.

\section{Results}
For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy. This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.  The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy. The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$. These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{SE_density.png}\\
\includegraphics[width=0.95\linewidth]{SE_z.png}
\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
\label{fig:spatial distribution}
\end{figure}

@@

Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars. In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}). Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances. In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models. However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies. To build towards this, we characterize the metal evolution and distributions in our galaxy below.

@@

We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF. We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element. This PDF is given as
\begin{align*}
  p(Z) = 
  \begin{cases}
    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right], 
    & Z < Z_{\rm{t}} \\
    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
    N p_o Z^{-\alpha},
    & Z > Z_{\rm{t}}
\end{cases}
\end{align*}
where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components. When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters. These conditions set $N$ and $p_o$ to 
\begin{equation}
N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
\end{equation}
and
\begin{equation}
p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
\end{equation}.

We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex. We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins. The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted. The log-normal + power-law PDF produces the best fit in nearly all cases.

We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases. These PDFs have been computed at an arbitrary single point in time, at 380 Myr. For clarity, we only show a subset of the 15 elements we follow. As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase. However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions. We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases. In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well. However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior. This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction. In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.

We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models. The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM. In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions. Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$. As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black). For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF. We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk. Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
\label{fig:log-normal}
\end{figure*}

@@

The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude. The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary. Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM. In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time. We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
